A Fredholm integral equation approach to computing Stokes eigenvalues in the plane

### 2019-03-21 doc/draft-01-stokes/01intro.tex
add files needed for latest tests

While type B methods for the
related ``buckling'' eigenvalue problem
have been considered previously,
these typically relied on first-kind integral
equation formulations of the underlying PDE,
i.e. formulations in which the BIE operator is
compact \cite{kitahara2014boundary,antunes2011buckling}.
%
This is unsatisfying from a theoretical
perspective, because such operators are never invertible
(though, they are injective precisely when $k^2$ is an
eigenvalue \cite{kitahara2014boundary,antunes2011buckling})
so that the relation between the non-invertibility of the
discrete system and the eigenvalues is obscured.
%
Further,
such representations create numerical challenges because
common measures of the ``non-invertibility'' of a matrix,
like the smallest singular value or the determinant, converge
rapidly to zero for all values of $k^2$ as the boundary is
refined. Therefore, the measure of whether $k^2$ is an
approximate eigenvalue is {\em relative to the current grid}
for first kind equations.

>>>>

While type B methods for the
related ``buckling'' eigenvalue problem
have been considered previously,
these typically relied on first-kind integral
equation formulations of the underlying PDE,
i.e. formulations in which the BIE operator is
compact \cite{kitahara2014boundary,antunes2011buckling}.
%
This is unsatisfying from a theoretical
perspective, because such operators are never invertible
(though, they are not injective precisely when $k^2$ is an
eigenvalue \cite{kitahara2014boundary,antunes2011buckling})
so that the relation between the non-invertibility of the
discrete system and the eigenvalues is obscured.
%
Further,
such representations create numerical challenges because
common measures of the ``non-invertibility'' of a matrix,
like the smallest singular value or the determinant, converge
rapidly to zero for all values of $k^2$ as the boundary is
refined. Therefore, the measure of whether $k^2$ is an
approximate eigenvalue is {\em relative to the current grid}
for first kind equations.

### 2019-03-21 doc/draft-01-stokes/02prelim.tex
add files needed for latest tests

Let $X$ be a Banach space equipped with a bilinear form ...

\note{Travis: put Fredholm alternative here}

@@

>>>>

We first recall some definitions.
Let $X$ and $Y$ be Banach spaces with a non-degenerate
bilinear form $\langle \cdot ,\cdot \rangle: X\times Y \to \C$.
\begin{itemize}
\item Two operators $\cA:X\to X$ and $\cB:Y\to Y$ are
adjoint operators if
$\langle A \phi,\psi \rangle = \langle \phi, B\psi \rangle$
for every $\phi \in X$ and $\psi \in Y$.
\item For an operator $\cM:X\to X$, we can define the range
  $R(\cM)$ as the set $\{\phi \in X: \exists \phi_0 \textrm{ with }
  \cM\phi_0 = \phi\}$ and the null space $N(\cM)$ as the
  set $\{\phi \in X: \cM \phi = 0 \}$.
\item An operator $\cA$ is said to be compact if
  $\overbar{\cA V}$ is a compact set for any

\item Given a subspace $V\subset X$,
  we can define the subspace $V^\perp\subset Y$ as the
  set $V^\perp = \{ \psi \in Y: \langle \phi,\psi \rangle = 0
  \textrm{ for each } \phi \in V \}$, with the analogous
  definition for subspaces of $Y$.
\end{itemize}

Operators of the form $\cI-\cA$
have existence and uniqueness properties analogous to
matrices. This is known as the Fredholm Alternative;
we present the version provided in \cite{colton1983integral}.

\begin{thrm}[Fredholm Alternative \cite{colton1983integral}]
  Let $X$ and $Y$ be Banach spaces and
  $\langle \cdot,\cdot \rangle: X\times Y \to \C$ be
  a bilinear form. Suppose that $\cA: X\to X$ and
  $\cB:Y \to Y$ are compact adjoint operators. Then
  $\dim N(\cI-\cA) = \dim N(\cI-\cB) \in \N$,
  $R(\cI-\cA) = N(\cI-\cB)^{\perp}$, and
  $R(\cI-\cB) = N(\cI-\cA)^\perp$.
\end{thrm}

@@

\begin{lem} \label{lem:compact-sd}
  Suppose that $\Omega$ is a bounded region with a $C^{2}$ boundary
  $\Gamma$. Then the operators $\cS$ and $\cD$ defined
  above are compact.
\end{lem}

Compactness is proved by considering the
asymptotic expansion of each kernel about
$\xx=\yy$ and noting that each is at most
weakly singular.
